Monitoring forest health using hyperspectral imagery: Does feature selection improve the performance of machine-learning techniques?

### 2020-05-01 docs/00-manuscripts/ieee/ieee-manuscript.tex
mention explicitly that all feature sets depend on the 2 m buffered values

\noindent To account for geometric offsets (which were reported with up to 1 m from \ac{ICGC}) within the hyperspectral data, a buffer of two meters around the centroid of each tree was used for extraction of the reflectance values.
A pixel was considered to fall into a tree's buffer zone if the centroid of the respective pixel was touched by the buffer.
In total, \(\frac{121*122}{2} = 7471\) NRIs were calculated due to the first four bands of the sensor being corrupted.

@@

\begin{itemize}
	\item The raw hyperspectral band information (HR): No feature engineering) %chktex 13
	\item Vegetation Indices (\ac{VI}): Expert-based feature engineering)
	\item Normalized Ratio Indices (\ac{NRI}): Data-driven feature engineering)
\end{itemize}

@@

\noindent The decision to use a buffer of 2 m for the extraction of an observation's reflectance value was a complex decision.
Due to the reported geometric offset of up to 1 m within the hyperspectral data, the possibility of assigning a value to an observation which would actually refer to a different observation was reasonably high.
By using a buffer of 2 meters (or more), the probability of including information from other trees into the final value increases, blurring the actual value of the tree observation.
However, the difference between single pixel values might often be higher than the difference between a smoothed value composed out of a buffer.
In our view using a buffer of 2 m was a good compromise between including information of too many surrounding trees and not accounting for the geometric offset at all.
Even though no results showing the influence of multiple buffer values on the extraction were provided, we hypothesize that the relationships between features would not change substantially, leading to the almost identical model results.

>>>>

\noindent To account for geometric offsets (which were reported with up to 1 m from \ac{ICGC}) within the hyperspectral data, a buffer of two meters around the centroid of each tree was used for extraction of the reflectance values.
These averaged reflectance values were used as the base to derive all feature sets.
A pixel was considered to fall into a tree's buffer zone if the centroid of the respective pixel was touched by the buffer.
In total, \(\frac{121*122}{2} = 7471\) NRIs were calculated due to the first four bands of the sensor being corrupted.

@@

\begin{itemize}
	\item The raw hyperspectral band information (HR): No feature engineering) %chktex 13
	\item Vegetation Indices (\ac{VIs}): Expert-based feature engineering)
	\item Normalized Ratio Indices (\ac{NRIs}): Data-driven feature engineering)
\end{itemize}

@@

\noindent The decision to use a buffer of two meters for the extraction of an observation's reflectance value was a complex decision.
Due to the reported geometric offset of up to 1 m within the hyperspectral data, the possibility of assigning a value to an observation which would actually refer to a different observation was reasonably high.
By using a buffer of two meters (or more), the probability of including information from other trees into the final value increases, blurring the actual value of the tree observation.
However, the difference between single pixel values might often be higher than the difference between a smoothed value composed out of a buffer.
In our view using a buffer of two meters was a good compromise between including information of too many surrounding trees and not accounting for the geometric offset at all.
Even though no results showing the influence of multiple buffer values on the extraction were provided, we hypothesize that the relationships between features would not change substantially, leading to the almost identical model results.
